% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\graphicspath{ {./images/} }

% Please include a clear, concise, and descriptive title
\title{Comp230 Handout} 

% Please do not change the subtitle
\subtitle{COMP230 Handout}

% Please put your student number in the author field
\author{1507516}

\begin{document}

\maketitle

\abstract{}


\section{Core Features}
For this component I have been working with a BA team to make their game multiplayer.

One of the core features of what I have been working on is a lobby system, this involves players being able to connect to a lobby and allowing the player to choose options for the game.

These options are:

\begin{itemize}
\item Player Colour
\item Player Name
\item Map
\end{itemize}

Another of the core features is networking player movement and player health.

\section{Unique selling points and Justification}
The game is a turn based first person shooter, where each player can move a unit until they run out of energy, then each player ends their turn. 
This type of game is much more fun against players than it is against AI. 

The game play is very similar to a game called valkyria chronicles.

\section{Market Research}

Having  multiplayer support will in most cases increase the sales of that game because playing games with friends can be more fun than playing games by yourself.

So having the free advertising that comes with multiplayer games will help with the success of the game.

Most of the popular games at the moment have some multiplayer aspect.

\section{Scope}
The networking is done through Unitys networking features, which means that a lot of the networking is done at quite a high level and a lot of it is abstracted away, which means that it is a lot easier to do than starting from scratch. 



\end{document}
